Instructions for ACL 2020 Proceedings

### 2019-12-03 reports/ACL2020 Paper/acl2020-paper.tex
Add accuracies for Experiment 1 (bert)

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}
\usepackage{times}
\usepackage{latexsym}
\renewcommand{\UrlFont}{\ttfamily\small}
\usepackage{booktabs}

% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

@@

\section{Experiments}
\subsection{Experiment 1: Impact of laughter}   % Vlad
% per dialogue act analysis
% compare impacts of CNN vs BERT
% for both AMI and SWDA

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}
\usepackage{times}
\usepackage{latexsym}
\renewcommand{\UrlFont}{\ttfamily\small}
\usepackage{booktabs}
\usepackage{graphicx}
% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

@@

\section{Experiments}
\subsection{Experiment 1: Impact of laughter}   % Vlad
In the first experiment we investigated whether laughter, as an example of a dialogue-specific signal, is a helpful feature for DAR.
Therefore, we train another version of each model: one containing laughters (L) and with laughters left out (NL), and compare their performances in DAR task.

\begin{table}
  \centering
  \begin{tabular}{@{}lll@{}}
    \toprule
                      & SWDA  & AMI-DA \\ \midrule
    \texttt{BERT-NL}  & 77.07 & 67.06       \\ 
    \texttt{BERT-L}   & 76.93 & 67.12       \\ \midrule
    \texttt{CNN-NL}   & 75.08 & 63.46        \\
    \texttt{CNN-L}    & 75.40 & 64.30        \\ \bottomrule

  \end{tabular}
  \caption{Comparison of models depending on using laughter in training phase.}
\end{table}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{img/bertLvsNL.pdf}
  \caption{Change in accuracy for each dialogue act. Positive changes when adding laughter are shown in blue. }
\end{figure*}
% TODO per dialogue act analysis
% DONE compare impacts of CNN vs BERT
% DONE for both AMI and SWDA
% ?
